---
title: "Adjusting linear model"
author: "Ariel Selles"
date: "June 13th, 2017"
output: 
  slidy_presentation: 
    css: slidy.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introducing the app

The app *Adjusting linear model* helps to compare two linear models on mtcars:

1. mpg ~ wt
2. mpg ~ wt + qsec

The comparison is made by ploting both models on a plane, after chosing a value for qsec. 

## Calculations

These are the coefficients for the first model:

```{r models, echo = FALSE}
# Linear models
model2 <- lm(data = mtcars, mpg ~ wt + qsec)
model1 <- lm(data = mtcars, mpg ~ wt)

model1$coef
```

And these, the ones related to the second one:

```{r model2, echo = FALSE, fig.height=4, fig.width=10}
model2$coef

qsInput <- 18.7
```

## Exemple

Selecting at the app the value **`r qsInput`**, these are the plots that you could see:

```{r plots, echo = FALSE, fig.height=4, fig.width=10}



# This prediction gives two points on the model plane, which allows us to calculate the new line
model2Pred <- predict(object = model2,
                      newdata = data.frame(wt = c(0, 6),
                                           qsec = c(qsInput, qsInput)))

# New intersection
a <- model2Pred[1]

# New slope
b <- (model2Pred[2] - model2Pred[1]) / 6

# Paint 2 plots
par(mfrow=c(1,2))

# Plots mtcars points (wt, mpg)
plot(x = mtcars$wt, y = mtcars$mpg, xlab="weight", ylab="miles per galon", main="Comparing models")

# Plots model line mpg ~ wt
abline(model1, col = "darkred", lwd = 2)

# Plots new model line: mpg ~ wt + qsec, with a fixed value of qsec
abline(a = a, b = b, col = "seagreen", lwd = 2)

# Plots mtcars points (qsec, mpg)
plot(x = mtcars$qsec, y = mtcars$mpg, xlab="sec per 1/4 mile", ylab="miles per galon", main="Selected qsec")

# Plots the line related to the selected value of qsec
abline(v = qsInput, col = "seagreen", lwd = 2)

```

## Summary

The app allows you to compare the two proposed models by adjusting the value of the parameter qsec.

You can run the application at https://arielselles.shinyapps.io/lmoncars/.

You can found the code of the application at https://github.com/arielselles/coursera-creating-apps.