---
title: "My Slidified Presentation"
author: "Ariel Selles"
date: "June 13th, 2017"
output: 
  slidy_presentation: 
    css: slidy.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Growth of Orange Trees

### About the slides

This slides show the growth of orange trees stored at the **Orange dataset**.

### The dataset

Mainly, the dataset stores *age* and *circumference* from **5 orange trees**, labeled *from 1 to 5*. 

The *age* is saved in *days* since December 31th of 1968, and the *circumference* in *millimeters*.

You can obtain more details by typing *?Orange* at your R console

***

```{r plotly}
suppressPackageStartupMessages(library(plotly))

plot_ly(data = Orange, 
        x = ~age, 
        y = ~circumference, 
        mode = "markers", 
        color = ~Tree, 
        type="scatter") %>%
    
    add_trace(x = ~age, 
        y = ~circumference, 
        mode = "lines", 
        color = ~Tree)
```

## Summary

At a first sight, it seems like all trees grow more or less the same along the whole period.

